Detecting Cosmic Reionization using Bi-Spectrum Phase

### 2018-05-01 ms_changes.tex
Update Acknowledgements section (Add RN, JM)

\begin{acknowledgments}
We acknowledge the insightful and helpful inputs from Gianni Bernardi, Judd Bowman, James Aguirre, Aaron Parsons, Jonathan Pober, Adam Beardsley, and Peter Williams that helped in the preparation of this manuscript. The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc. We acknowledge support from the Royal Society and the Newton Fund under grant NA150184.
\end{acknowledgments}

>>>>

\begin{acknowledgments}
We acknowledge the insightful and helpful inputs from \added{Rajaram Nityananda}, Gianni Bernardi, Judd Bowman, James Aguirre, Aaron Parsons, \added{James Moran,} Jonathan Pober, Adam Beardsley, and Peter Williams that helped in the preparation of this manuscript. The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc. We acknowledge support from the Royal Society and the Newton Fund under grant NA150184.
\end{acknowledgments}
